Biogeography of crop progenitors and wild plant resources during the transition to agriculture in West Asia

### 2024-11-27 analysis/analysis.qmd
Remove redundant chunk

```{r niche_model_test}
# Predict model on test data and assess performance
# TODO: model performance assessments:
# - [ ] R2
# - [ ] Boyce index
# - [x] AUC, ROC, AUC-ROC, AUC-PRG ?
# - [ ] TSS
# flora <- flora |>
#   mutate(
#     niche_test = map2(niche, occ_split, \(x, y) augment(x, testing(y))),
#     niche_test_roc_auc = map_dbl(niche_test, function(x) {
#       roc_auc(x, present, .pred_TRUE)$.estimate
#     }),
#     niche_test_accuracy = map_dbl(niche_test, function(x) {
#       accuracy(x, present, .pred_class)$.estimate
#     })
#   )

# TODO: filter to minimum accuracy? 0.85? 0.9? 0.95?
```

@@

# TODO: very high memory usage
flora <- flora |>
  mutate(
    prediction = map(niche, \(mod, obj) predict(obj, extract_fit_engine(mod)), 
                     obj = climate_pred)
  )
```

>>>>

@@

# NOTE: very high memory usage
flora <- flora |>
  mutate(
    prediction = map(niche, \(mod, obj) predict(obj, extract_fit_engine(mod)), 
                     obj = climate_pred)
  )
```
